Gráfico de control T2 Hotelling para variables cualitativas

### 2021-11-20 ArticleHotellingACM/ArticleHotellingACM.Rmd
Add J

---
title: Gráfico de control T2 Hotelling para variables cualitativas
author:
  - name: Wilson Rojas-Preciado
    affil: 1,2
    orcid: 0000-0003-1614-698X
  - name: Mauricio Rojas-Campuzano
    affil: 3
    orcid: 0000-0001-8000-9432
  - name: Purificación Galindo-Villardón
    affil: 2
    orcid: 0000-0001-6977-7545
  - name: Omar Ruiz-Barzola
    affil: 3
    orcid: 0000-0001-8206-1744
  - num: 1
    address: |
      Universidad Técnica de Machala - 
      Machala, Ecuador
    email: wrojas@utmachala.edu.ec
  - num: 2
    address: |
      Universidad de Salamanca
      Salamanca, España
    email: wrojas@usal.es
  - num: 2
    address: |
      Escuela Superior Politécnica del Litoral
      Gayaquil, Ecuador
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  wrojas@utmachala.edu.ec; Tel.: +593-992-83-3719
journal: water
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  Abstract
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
authorcontributions: |
conflictsofinterest: |
sampleavailability: |
abbreviations:

>>>>

---
title: Gráfico de control T2 Hotelling para variables cualitativas
author:
  - name: Wilson Rojas-Preciado
    affil: 1,2
    orcid: 0000-0003-1614-698X
  - name: Mauricio J. Rojas-Campuzano
    affil: 3
    orcid: 0000-0001-8000-9432
  - name: Purificación Galindo-Villardón
    affil: 2
    orcid: 0000-0001-6977-7545
  - name: Omar Ruiz-Barzola
    affil: 3
    orcid: 0000-0001-8206-1744
  - num: 1
    address: |
      Universidad Técnica de Machala - 
      Machala, Ecuador
    email: wrojas@utmachala.edu.ec
  - num: 2
    address: |
      Universidad de Salamanca
      Salamanca, España
    email: wrojas@usal.es
  - num: 2
    address: |
      Escuela Superior Politécnica del Litoral
      Gayaquil, Ecuador
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  wrojas@utmachala.edu.ec; Tel.: +593-992-83-3719
journal: water
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  Abstract
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
authorcontributions: |
conflictsofinterest: |
sampleavailability: |
abbreviations:

### 2021-11-20 ArticleHotellingACM/ArticleHotellingACM.tex
upd2
Add J

% Authors, for the paper (add full first names)
\Author{Wilson
Rojas-Preciado$^{1,2}$\href{https://orcid.org/0000-0003-1614-698X}{\orcidicon}, Mauricio
Rojas-Campuzano$^{3}$\href{https://orcid.org/0000-0001-8000-9432}{\orcidicon}, Purificación
Galindo-Villardón$^{2}$\href{https://orcid.org/0000-0001-6977-7545}{\orcidicon}, Omar
Ruiz-Barzola$^{3}$\href{https://orcid.org/0000-0001-8206-1744}{\orcidicon}, $^{}$, $^{}$, $^{}$}

% Authors, for metadata in PDF
\AuthorNames{Wilson Rojas-Preciado, Mauricio
Rojas-Campuzano, Purificación Galindo-Villardón, Omar
Ruiz-Barzola, , , }

>>>>

% Authors, for the paper (add full first names)
\Author{Wilson
Rojas-Preciado$^{1,2}$\href{https://orcid.org/0000-0003-1614-698X}{\orcidicon}, Mauricio
J.
Rojas-Campuzano$^{3}$\href{https://orcid.org/0000-0001-8000-9432}{\orcidicon}, Purificación
Galindo-Villardón$^{2}$\href{https://orcid.org/0000-0001-6977-7545}{\orcidicon}, Omar
Ruiz-Barzola$^{3}$\href{https://orcid.org/0000-0001-8206-1744}{\orcidicon}, $^{}$, $^{}$, $^{}$}

% Authors, for metadata in PDF
\AuthorNames{Wilson Rojas-Preciado, Mauricio J.
Rojas-Campuzano, Purificación Galindo-Villardón, Omar
Ruiz-Barzola, , , }
